\SW: II. New lens candidates from the CFHTLS discovered through citizen science

### 2015-04-15 doc/sw-cfhtls.tex
fixed and closed #129

The last few decades have seen a rise in the discoveries of strong
gravitational lenses owing to the plethora of interesting applications
lenses have in astrophysics and cosmology. Strong lenses are routinely
used to probe the dark matter distribution from galaxy
\citep[e.g.][]{Koopmans2006,Barnabe2009,Sonnenfeld2015} to groups-cluster
scales
\citep[e.g.][]{Limousin2008,Zitrin2011,Oguri2012,More2012,Newman2013}, to
study distant young galaxies by using the lensing magnification as a
natural telescope \citep[e.g.][]{Zitrin2009,Zheng2012,Whitaker2014}, to
test the cosmological model by constraining cosmological parameters such
as the Hubble constant and dark energy
\citep[e.g.][]{Suyu2010,Collett2012,Collett2014,Sereno2014} and many more. Strong
lenses are rare since a foreground massive object needs to be
sufficiently aligned with a distant background source to produce
multiple images. Nevertheless, systematic lens searches have led to the
discovery of over 500 lenses till
date\footnote{http://masterlens.astro.utah.edu}.

@@

The \cfhtls is a photometric survey in five optical bands
($u^*g'r'i'z'$) carried out with the wide-field imager MegaPrime which
has a 1~deg$^2$ field-of-view and a pixel size of 0.186\arcsec
\citep{Gwyn2012}. The \cfhtls \textsc{WIDE} covers a total
non-overlapping area of 150~deg$^2$ on the sky and consists of four
fields W1, W2, W3 and W4. The field W1 has the largest sky coverage of
63.65~deg$^2$. The fields W2 and W4 have similar sky coverages of
20.32~deg$^2$ and 20.02~deg$^2$, respectively\footnote{These numbers are
estimated from http://terapix.iap.fr/cplt/table\_syn\_T0006.html}.  The
field W3 has a sky coverage of 42.87~deg$^2$ and is more than twice as
large as W2 and W4.

The \cfhtls imaging is very homogeneous and has good image quality. Most
of the lensed arcs are much brighter in the $g$ band thus, deep imaging
in this band is desirable. The limiting magnitude is 25.47 for the $g$
band which goes the deepest among all of the five bands. The mean seeing
in the $g$ band is 0.78\arcsec. The zero point to convert flux to AB
magnitude for all bands is 30. These characteristics make \cfhtls ideal
to do visual inspection for finding lenses.  We use the stacked images
from the final T0007 release taken from the Terapix
website\footnote{{http://terapix.iap.fr/cplt/T0006-doc.pdf}} for this
work.

@@

The work by \citet{Maturi2014} used the arc finding code of
\citet{Seidel2007} and color properties of typical arcs to optimize arc
detection. This new approach was tested on the CFHTLS-Archive-Research
Survey \citep[CARS,][]{Erben2009} which covers an area of 37~sq.~deg
only and this entire data was also visually inspected by the authors to
estimate completeness and purity of their robotic search. They found 29
candidates with the robotic search alone and 41 candidates through pure
visual inspection some of which are known from previous searches. Most
of these candidates are medium-low
probability\footnote{http://www.ita.uni-heidelberg.de/˜maturi/Public/arcs}.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/dlnp_skill.pdf}
\caption{ \label{fig:skilldlnp}
Skill of the volunteers and $\Delta\log(P)$ given a lens or not a lens in
an image as a function of $P_{\rm L}$ and $P_{\rm D}$. These
quantities indicate the ability of the volunteers but do not have a simple
linear relation with $P_{\rm L}$ and $P_{\rm D}$.  
\question{AM}{PJM, should we just use power everywhere instead of the
$\Delta\log(P)$? This figure and this section still needs to be
polished. }
}
\end{center}
\end{figure*}

>>>>

The last few decades have seen a rise in the discoveries of strong
gravitational lenses owing to the plethora of interesting applications
lenses have in astrophysics and cosmology. Strong lenses are routinely
used to probe the dark matter distribution from galaxy
\citep[e.g.][]{Koopmans2006,Barnabe2009,Sonnenfeld2015} to groups-cluster
scales
\citep[e.g.][]{Limousin2008,Zitrin2011,Oguri2012,More2012,Newman2013}, to
study distant young galaxies by using the lensing magnification as a
natural telescope \citep[e.g.][]{Zitrin2009,Zheng2012,Whitaker2014}, to
test the cosmological model by constraining cosmological parameters such
as the Hubble constant and dark energy
\citep[e.g.][]{Suyu2010,Collett2012,Collett2014,Sereno2014} and many more. Strong
lenses are rare since a foreground massive object needs to be
sufficiently aligned with a distant background source to produce
multiple images. Nevertheless, systematic lens searches have led to the
discovery of over 500 lenses till
date\footnote{http://admin.masterlens.org/index.php}.

@@

The \cfhtls is a photometric survey in five optical bands
($u^*g'r'i'z'$) carried out with the wide-field imager MegaPrime which
has a 1~deg$^2$ field-of-view and a pixel size of 0.186\arcsec
\citep{Gwyn2012}. The \cfhtls \textsc{WIDE} covers a total
non-overlapping area of 150~deg$^2$ on the sky and consists of four
fields W1, W2, W3 and W4. The field W1 has the largest sky coverage of
63.7~deg$^2$. The fields W2 and W4 have similar sky coverages of
22.6~deg$^2$ and 23.3~deg$^2$, respectively\footnote{These numbers are
estimated from http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}.  The
field W3 has a sky coverage of 44.2~deg$^2$ and is more than twice as
large as W2 and W4.

The \cfhtls imaging is very homogeneous and has good image quality. Most
of the lensed arcs are much brighter in the $g$ band thus, deep imaging
in this band is desirable. The limiting magnitude is 25.47 for the $g$
band which goes the deepest among all of the five bands. The mean seeing
in the $g$ band is 0.78\arcsec. The zero point to convert flux to AB
magnitude for all bands is 30. These characteristics make \cfhtls ideal
to do visual inspection for finding lenses.  We use the stacked images
from the final T0007 release taken from the Terapix
website\footnote{{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}} for this
work.

@@

The work by \citet{Maturi2014} used the arc finding code of
\citet{Seidel2007} and color properties of typical arcs to optimize arc
detection. This new approach was tested on the CFHTLS-Archive-Research
Survey \citep[CARS,][]{Erben2009} which covers an area of 37~sq.~deg
only and this entire data was also visually inspected by the authors to
estimate completeness and purity of their robotic search. They found 29
candidates with the robotic search alone and 41 candidates through pure
visual inspection some of which are known from previous searches. Most
of these candidates are medium-low
probability\footnote{http://www.ita.uni-heidelberg.de/~maturi/Public/arcs}.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/dlnp_skill.pdf}
\caption{ \label{fig:skilldlnp}
Skill of the volunteers and $\Delta\log(P)$ given a lens or not a lens in
an image as a function of $P_{\rm L}$ and $P_{\rm D}$. These
quantities indicate the ability of the volunteers but do not have a simple
linear relation with $P_{\rm L}$ and $P_{\rm D}$.  
}
\end{center}
\end{figure*}
